---
title: "Creating a Wind Rose in R"
author: '-'
date: "March 30, 2018"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{Creating a windRose plot}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
# This vignette performs two purposes.
# (1) Provide a detailed description of the nuiances of the openair package for educational purposes.
# (2) Each example can doubles as a unit test.  When the vignette is knitted, it is easy to tell if and where the code breaks.

knitr::opts_chunk$set(echo = TRUE)
```


## Getting Started with windRose - The default example

The default example wind rose is straightforward to plot.

```{r basic windrose}
library(openair)
windRose(mydata)
```


## Less is More - A Test Wind Rose

This example demonstrates a minimal test wind rose to clarify how the wind rose function works.

windRose requires data to be formatted as a dataframe.  
By default windRose expects the dataframe to have two columns: 
one named ***ws*** for wind speed and another named ***wd*** for wind direction. 

The following example creates such a dataframe called ***testData***.  
Using windRose in a minimal configuration,  ***testData*** is plotted with a a single spoke radiating at 90 degrees.


```{r wind direction windrose}
library(openair)
testData <- data.frame(ws = c(1,1), wd = c(90,90))
windRose(testData, 
         breaks = 1,                     # breaks = 1 disables wind speed intervals
         angle = 30,                     # sets the angle of the spoke to 15 degrees
         paddle = FALSE,                 # draws spokes as wedges
         annotate = FALSE,               # removes default annotations
         col = "blue",                   # draw a blue spoke  
         grid.line = list(max = 100),    # limits grid lines to 100%
         key = FALSE,                    # remove the key  
         main = "Test Wind Rose")

```
